Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-24 netsoft_paper.tex
the third edition

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_app}
\caption{Illustration of rate-limiting for a certain host}
\label{fig:mft_qos_rate_app}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/evaluation_classification}
\caption{Result of Multiple Table Performance Evaluation}
\label{fig:evaluation_classification}
\end{figure}

@@

As shown in Fig. \ref{fig:qos_limit_host}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service. And the OpenFlow-enable switch use the the Edge-Core AS5712-54X switch that operating system is PicOS TM r2.6.

We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds. In the beginning, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps.
At \nth{10} seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps. Then we can find out the bandwidth from this host is decrease and be limited to about 1024Kbps immediately.

@@

There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source. We integrated with application identification to classify each flow belongs what the application is, consequently.
In our experiment environment, as shown in Fig.9. We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications. Application identification system will upload the result of identification to database. Then the controller will get the result from the database and update the flow information of application. Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain. Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
As shown in Figure.? In the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps. At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain. Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately. Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_app}
\caption{Illustration of rate-limiting for a certain application.}
\label{fig:mft_qos_rate_app}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/evaluation_classification}
\caption{Evaluation of Application Identification.}
\label{fig:evaluation_classification}
\end{figure}

@@

As shown in Fig. \ref{fig:class_classifying}, The NFV controller run on the Dell PowerEdge R630 Rack Server, and would excute the QoS service. And the OpenFlow-enable switch use the the Edge-Core AS5712-54X switch that operating system is PicOS TM r2.6.

We used a desktop computer to be the experimental host and record the bandwidth in every 2 seconds. As shown in Fig \ref{fig:qos_limit_host}, we start downloading the file without limiting and the rate is between 190000 Kbps to 410000 Kbps in the beginning.
At \nth{10} seconds, we wanted to limit this host’s bandwidth to 1024Kbps and we added the rule the destination MAC address is matching this desktop computer with a meter of 1024Kbps. Then we can find out the bandwidth from this host is decrease and be limited to about 1024Kbps immediately.

@@

There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source. We integrated with application identification to classify each flow belongs what the application is, consequently.
In our experiment environment, as shown in Fig. \ref{fig:class_classifying}. We use a mirror switch to replicate the whole traffic form SDN switch and provide the application identification system to classify the flows belong which applications. Application identification system will upload the result of identification to database. Then the controller will get the result from the database and update the flow information of application. Therefore, we can use the flow information (5 tuple and the result of identification) to complete our limitation to application.
We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain. Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
As shown in Figure. \ref{fig:mft_qos_rate_domain_app}, in the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps. At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain. Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately. Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.
